Model for DES Type Ia Supernova Cosmology Analysis

### 2016-05-08 tex/toy.tex

\subsection{Case Typed}
For Case Typed the likelihood is
\begin{align}
\mathcal{L}(T_o,z_o,c_o | S_c, S_T, z, X) & =  \int dL \sum_i p(T_o,z_o,c_o | T_i, L, S_c, S_T, z, X) p(L |  T_i,  S_c, S_T, z, X) P(T_i|S_c, S_T, z, X).
\end{align}
We assume that the observations give a perfect measurement of type and redshift,
so that
\begin{align}
p(T_o|T) & =\delta(T_o-T)\\
p(z_o|z) & =\delta(z_o-z);
\end{align}
$T$ and $z$ are no longer probabilistic but are fixed.
Then
\begin{align}
\mathcal{L}(T_o,z_o,c_o | S_c, S_T, z, X) & =  \int dL\, p(c_o | T=T_o, L, S_c, S_T, z=z_o, X) p(L| T=T_o, S_c, S_T, z=z_o, X)  P(T_o|S_c, S_T, z=z_o, X) \\
&= \int dL\, \frac{ p(c_o, S_c, S_T | T=T_o, L, z=z_o, X) }{P(S_c, S_T, | T=T_o, L,  z=z_o, X) }
\frac{p(L, S_c, S_T | T=T_o, z=z_o, X)}{P(S_c, S_T| T=T_o,  z=z_o, X)}
\frac{p(T_o, S_c, S_T | z=z_o, X)}{P(S_c, S_T| z=z_o, X)} \\
&= \frac{\int dL\, p(L|T_o, z=z_o, X) P(T_o|z=z_o, X) p(c_o, S_c, S_T | T=T_o, L, z=z_o, X)}{P(S_c, S_T| z=z_o, X)}\\
&= \frac{\int dL\, p(L|T_o, z=z_o, X) P(T_o|z=z_o, X) p(c_o | T=T_o, L, z=z_o, X)}{P(S_c, S_T| z=z_o, X)}.
\end{align}

The  normalization term sums/integrates over all possible observed types/counts 
\begin{align}
P(S_c, S_T| z=z_o, X) & =\sum_i \int dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X) \\
% & =\sum_i \int_{-\infty}^{\infty} dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X) \\
%& = \sum_i \int_{c_T}^{\infty} dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X)\\
& = \sum_i  P(T_i|z=z_o, X)\int dL\, p(L|T_i, z=z_o, X)  \left[\int dc_o\,  p(c_o,S_c, S_T | T=T_i, L, z=z_o, X)\right].
\end{align}

>>>>

\subsection{Case Typed}
For Case Typed the likelihood is
\begin{align}
\mathcal{L}(T_o,z_o,c_o | S_c, S_T, z, X) & =  \int dL \sum_i p(T_o,z_o,c_o | T_i, L, S_c, S_T, z, X) p(L |  T_i,  S_c, S_T, z, X) P(T_i|S_c, S_T, z, X).
\end{align}
We assume that the observations give a perfect measurement of type and redshift,
so that
\begin{align}
p(T_o|T) & =\delta(T_o-T)\\
p(z_o|z) & =\delta(z_o-z);
\end{align}
$T$ and $z$ are no longer probabilistic but are fixed.
Then
\begin{align}
\mathcal{L}(T_o,z_o,c_o | S_c, S_T, z, X) & =  \int dL\, p(c_o | T=T_o, L, S_c, S_T, z=z_o, X) p(L| T=T_o, S_c, S_T, z=z_o, X)  P(T_o|S_c, S_T, z=z_o, X) \\
&= \int dL\, \frac{ p(c_o, S_c, S_T | T=T_o, L, z=z_o, X) }{P(S_c, S_T, | T=T_o, L,  z=z_o, X) }
\frac{p(L, S_c, S_T | T=T_o, z=z_o, X)}{P(S_c, S_T| T=T_o,  z=z_o, X)}
\frac{p(T_o, S_c, S_T | z=z_o, X)}{P(S_c, S_T| z=z_o, X)} \\
&= \frac{\int dL\, p(L|T_o, z=z_o, X) P(T_o|z=z_o, X) p(c_o, S_c, S_T | T=T_o, L, z=z_o, X)}{P(S_c, S_T| z=z_o, X)}.%\\
%&= \frac{\int dL\, p(L|T_o, z=z_o, X) P(T_o|z=z_o, X) p(c_o | T=T_o, L, z=z_o, X)}{P(S_c, S_T| z=z_o, X)}.
\end{align}

The photometric and spectroscopic sample selections can be treated as efficiencies $\epsilon_c$, $\epsilon_T$ as
\begin{align}
p(c_o, S_c, S_T | T=T_o, L, z=z_o, X) & = \int ds\, p(c_o, s, S_c, S_T | T=T_o, L, z=z_o, X) \\
 & =p(c_o, S_c | T=T_o, L, z=z_o, X)  \int ds\,  p(s, S_T | T=T_o, L, z=z_o, X) \\
 & = \epsilon_c(c_o) p(c_o| T=T_o, L, z=z_o, X)  \int ds\, \epsilon_T(c_o, s)  p(s | T=T_o, L, z=z_o, X) \\
 & \approx \epsilon_c(c_o)   \epsilon_T(c_o, s_\star) p(c_o| T=T_o, L, z=z_o, X).
\end{align}
where the supernova signal in the spectrum $s$ is not extracted and we make the approximation $ p(s | T=T_o, L, z=z_o, X)  = \delta(s-s_\star)$
and $s_\star(t_T; T=T_o, L, z=z_o, X)$ is the expected signal.

The  normalization term sums/integrates over all possible observed types/counts 
\begin{align}
P(S_c, S_T| z=z_o, X) & =\sum_i \int dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X) \\
% & =\sum_i \int_{-\infty}^{\infty} dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X) \\
%& = \sum_i \int_{c_T}^{\infty} dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X)\\
& = \sum_i  P(T_i|z=z_o, X)\int dL\, p(L|T_i, z=z_o, X)  \left[\int dc_o\,  p(c_o,S_c, S_T | T=T_i, L, z=z_o, X)\right] \\
& \approx  \sum_i   P(T_i|z=z_o, X)\int dL\, p(L|T_i, z=z_o, X)  \left[ \int dc_o\, \epsilon_c(c_o)  \epsilon_T(c_o, s_\star)  p(c_o| T=T_o, L, z=z_o, X)  \right] .
\end{align}
